---
title: 'National Cyber Power Index (NCPI):      
Background Analsyis'
author: "Belfer Cyber Power Project"
date: "9 June 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# load packages:
library(tidyverse) # ggplot2, tidyr, ...
library(GGally)
library(ggrepel)
library(ggcorrplot)


# load data
CPI_scores <- readRDS("../../data/data_for_modelling/CPI_scores.rds") %>%
    filter(country != "North Korea") # remove North Korea for now because of missing information


# Define color palette:
# order: black, female, male, other, highlight
my_palette <- c("#383D3B", "#52DEE5", "#B3B3F1", "#FF220C", "#BEEF9E")
# my_palette <- c(
#   `black` = "#383D3B",
#   `male` = "#52DEE5", 
#   `female` = "#B3B3F1", 
#   `highlight` = "#FF220C",
#   `other` = "#BEEF9E")


crimson_theme <- function() {
  # font <- "Georgia"   #assign font family up front
  theme_minimal() %+replace%    #replace elements we want to change
  theme(
    # add border 1)
    panel.border = element_rect(colour = "blue", fill = NA, linetype = 2),
    # color background 2)
    panel.background = element_rect(fill = "aliceblue"),
    # modify grid 3)
    panel.grid.major.x = element_line(colour = "#A51C30", linetype = 3, size = 0.5),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y =  element_line(colour = "#A51C30", linetype = 3, size = 0.5),
    panel.grid.minor.y = element_blank(),
    
    # modify text, axis and colour 4) and 5)
    # axis.text = element_text(colour = "black", face = "italic", family = "Times New Roman"),
    # axis.title = element_text(colour = "black", family = "Times New Roman"),
    axis.ticks = element_line(colour = "black"),
    # legend at the bottom 6)
    legend.position = "bottom"
  )
}

```


# Intro

This paper explains the methodology behind the National Cyber Power Index. 


**Theory**

We identify seven objectives in cyber space:  

(1) Surveillance = Surveilling and Monitoring Domestic Groups  
(2) Defense = Strengthening and Enhancing National Cyber Defenses  
(3) Information Control = Controlling and Manipulating the Information Environment  
(4) Intelligence = Foreign Intelligence Collection for National Security  
(5) Commercial = Commercial Gain of Enhancing Domestic Industry Growth  
(6) Offense = Destroying or Disabling Adversary Infrastructure  
(7) Norms = Defining International Cyber Norms and Standards 


For each objective, we measure a states' capabilities and intent to achieve said obejctive. 

Each objective is weighted equally, therefore a country's national cyber power score is the average sum score of each objective. 


**Formula**
<!-- http://www.math.mcgill.ca/yyang/regression/RMarkdown/example.html -->


$$NCPI = \frac{1}{7}\sum_{x=1}^7 Capability_x*Intent_x$$

**Data**

We have 30 countries (observations) and for each country we have:
- 36 capability indicators (on continous and ordinal metrics)
- 42 intent indicators (dichotomous)


<!-- add \newpage or \pagebreak for new page -->

\newpage

# Construction of Intent indicators

We have measured a country's intent to pursue the seven objectives in cyber space

To meaningfully compare a country’s intent, we created an approach that scored five factors that account for the overall quality of their cyber intent, which we have termed “strategy quality score”. These are:

1.	How long a country has had a national cyber strategy;
2.	How frequently the country updates the strategy;
3.	The length of time since the last update;
4.	Quality of the strategy document as assessed by the team; and,
5.	Whether the national government has allocated financial resources to meet cyber objectives.

**Example: surveillance**

*For the objective surveillance we assess whether:* 

- Does the country have at least one police or law enforcement agency with specialist cyber-crime expertise or that encourages citizens to report cyber-crime?
Yes = 1 No = 0

Is cyber crime, cyber terrorism, or domestic surveillance via cyber means referred to within the country's domestic counter-terrorism or homeland security strategy or plan?
-Yes = 1 No = 0

Consistency of objective: is it pursued in >1 Strategy?
- Objective present in >1 strategy = 1 No = 0

Observed in attributed cyber attack
- Observed in 1 or more attack = 1 No = 0

? If surveillance activity is acknowledged in the country's national cyber strategy: include strategy quality score
- Score from 1 to 0 

? If surveillance activity is acknowledged in the country's national cyber strategy: include financial score
- Increased cyber funding announced: Yes = 1 No = 0

*Objective unrelated assessment*
? Strategy Quality Metric
-range from 0 to 1 

? Finance
-Yes = 1 No = 0

*Score for surveillance objective*

Score Surveillance = Surveillance Sum + Strategy Quality Metric + Finance

percentage surveillance = actual score surveillance / max points score surveillance

Note: In the current version there is a problem with the percentage calculation!


**Open questions**

1. logic behind the percentage calculation
2. discussion of the effect size
3. range instead of yes / no
4. aggregation of objective independent intent indicators






\newpage

# Construction of Capability indicators  

**Step 1: datacollection**

We have collected indicators of cyber power. Roughly a third of the indicators have been sourced in house


**Step 1: subsetting the data**

We have subsetted the data, so that for each objective we have a separate data set.  
Each dataset contains indicators that measure said objective. 
Some indicators are a measure for different objectives and are therefore counted multiple times. 

The latter is true for the following indicators

- laws (three times), 
- surveillance_firm (twice), 
- socials_use (twice),
- internet_use (three times),
- human_capital (three times),
- cyber_firm (twice),
- infocomm_import (two times),
- tech_firm (three times)
- tech_export (four times),
- cybermil_people (twice),
- web_alexa (twice)  

**Step 2: normalize**

We have normalized the indicators using z-scores. 
After performing normalization, the data have a common scale with a mean of 50 and a standard deviation of 20. 
Since we have extreme values in our dataset, such as exceptional performance, z-score standardization is to prefer over min-max standardization  

**Step 3: aggregate**

Given that we only have 30 observations (and 36 indicators) we can not apply classical parametric psychometric techniques (such as IRT ).
To aggregate the indicators in a composite scale, for each country we have simply computed the mean of the sum of the indicators (per each objective).

There is an alternative (more fancy) aggregation method which we plan to test as well: 
Alternatively, we could  use a method from the Gifi framework, as these techniques are exploratory (and nonparametric in some sense). To be precise, we could run a type of PCA called princals (see princals() function in the Gifi package) which is a
PCA for mixed scale levels. The details are the Chapter 8 of Patrick Mair's book "Modern Psychometrics with R" (Section 8.2.3 contains what we need), available through Hollis.
R code can be found here:
https://github.com/pmair78/MPsychoR
This method gives  (aggregate) PC scores which can then be used for subsequent modeling. If the indicators are unidimensional, you can use the scores from the first component; if it turns out that two dimensions are needed, then we use the first 2 PC scores, etc. (Input from Patrick Mair)

<!-- (mair@fas.harvard.edu) -->


## Pairwise correlation of indicators

 
**1 Surveillance**  

Indicators:  
- laws (""POS""),  
- attack_surveillance (""POS""),  
- freedom_net (""POS""),  
- surveillance_firm  (""POS""),  
- socials_use (""POS""),   
- internet_use (""POS"")

```{r , echo=FALSE, message=FALSE, warning=FALSE}

CPI_scores %>% 
  ggpairs(columns = c("laws", "attack_surveillance", "freedom_net", "surveillance_firm", "socials_use", "internet_use")) 

  ggcorr(CPI_scores[, c("laws", "attack_surveillance", "freedom_net", "surveillance_firm", "socials_use", "internet_use")], method = c("pairwise", "pearson"), label=T, hjust = 0.75, size = 3, color = "grey50")



```

\newpage

**2 Defense**  

Indicators:    
- laws(""POS""),  
- shodan (""NEG""),   
- human_capital (""POS""),   
- cyber_firm (""POS""),   
- computer_infection (""NEG""),   
- mobile_infection (""NEG""),   
- internet_use (""NEG"") [REMOVE?],   
- broadband_speed (""POS""),   
- mobile_speed (""POS""),   
- ICT imports (""NEG""),  
- CERTS (""POS"")


```{r , echo=FALSE, message=FALSE, warning=FALSE}

CPI_scores %>% 
  ggpairs(columns = c("laws", "shodan",  "human_capital", "cyber_firm", "computer_infection", "mobile_infection", "internet_use", "broadband_speed", "mobile_speed", "infocomm_imp", "CERTS"))

  ggcorr(CPI_scores[, c("laws", "shodan",  "human_capital", "cyber_firm", "computer_infection", "mobile_infection", "internet_use", "broadband_speed", "mobile_speed", "infocomm_imp", "CERTS")], method = c("pairwise", "pearson"), label=T, hjust = 0.75, size = 3, color = "grey50")

```

\newpage

**3 Information Control**  

Indicators:
- attack_manipulation (""POS""),  
- internet_use (""POS""),    
- socials_use (""POS""),    
- news_alexa (""POS""),   
- web_alexa (""POS""),   
- removal_google (""POS"")



```{r , echo=FALSE, message=FALSE, warning=FALSE}

CPI_scores %>% 
  ggpairs(columns = c("attack_control", "internet_use", "socials_use", "news_alexa", "web_alexa", "removal_google"))

  ggcorr(CPI_scores[, c("attack_control", "internet_use", "socials_use", "news_alexa", "web_alexa", "removal_google")], method = c("pairwise", "pearson"), label=T, hjust = 0.75, size = 3, color = "grey50")

```

\newpage

**4 Intelligence**  

Indicators: 

- attack_intelligence (""POS""),   
- tech_export (""POS""),   
- human_capital (""POS""),   
- cybermil_people (""POS""),   
- tech_firm (""POS""),   
- surveillance_firm (""POS"")


```{r , echo=FALSE, message=FALSE, warning=FALSE}

CPI_scores %>% 
  ggpairs(columns = c("attack_intelligence", "tech_export", "human_capital", "cybermil_people", "tech_firm", "surveillance_firm"))

ggcorr(CPI_scores[, c("attack_intelligence", "tech_export", "human_capital", "cybermil_people", "tech_firm", "surveillance_firm")], method = c("pairwise", "pearson"), label=T, hjust = 0.75, size = 3, color = "grey50")
                     

```


**5 Commercial**  

Indicators: 
- attack_commercial  (""POS""),    
- tech_firm  (""POS""),    
- human_capital  (""POS""),    
- cyber_firm  (""POS""),    
- web_alexa  (""POS""),   
- ecommerce_capita  (""POS""),   
- tech_export (""POS""),  
- infocomm_imp (""NEG""),  
- patent_app_capita (""POS"")


```{r , echo=FALSE, message=FALSE, warning=FALSE}

CPI_scores %>% 
  ggpairs(columns = c("attack_commercial", "tech_firm", "human_capital", "cyber_firm", "web_alexa", "ecommerce_capita", "tech_export", "infocomm_imp", "patent_app_capita"))

ggcorr(CPI_scores[, c("attack_commercial", "tech_firm", "human_capital", "cyber_firm", "web_alexa", "ecommerce_capita", "tech_export", "infocomm_imp", "patent_app_capita")], method = c("pairwise", "pearson"), label=T, hjust = 0.75, size = 3, color = "grey50")

                     

```


**6 Offense**  
Indicators:  

- attack_offense (""POS""),  
- tech_export  (""POS""),  
- cybermil_people (""POS""),   
- military_strategy (""POS""),   
- cyber_command (""POS"")


```{r , echo=FALSE, message=FALSE, warning=FALSE}

CPI_scores %>% 
  ggpairs(columns = c("attack_offense", "tech_export", "cybermil_people", "military_strategy", "cyber_command"))

ggcorr(CPI_scores[, c("attack_offense", "tech_export", "cybermil_people", "military_strategy", "cyber_command")], method = c("pairwise", "pearson"), label=T, hjust = 0.75, size = 3, color = "grey50")
                     

```

**7 Norms**  

Indicators:  
- laws (""POS""), 
- int_agreement (""POS""),  
- bilat_agreement ("POS"),  
- infocomm_imp  (""NEG""),   
- tech_firm (""POS""),   
- tech_export (""POS"")

```{r , echo=FALSE, message=FALSE, warning=FALSE}

CPI_scores %>% 
  ggpairs(columns = c("laws", "muli_agreement", "bilat_agreement", "infocomm_imp", "tech_firm", "tech_export", "softpower"))

ggcorr(CPI_scores[, c("laws", "muli_agreement", "bilat_agreement", "infocomm_imp", "tech_firm", "tech_export", "softpower")], method = c("pairwise", "pearson"), label=T, hjust = 0.75, size = 3, color = "grey50")

                     
```


# Sensitivity analysis

We compare the capability score to the GDP per capita.

```{r , echo=FALSE, message=FALSE, warning=FALSE}

ggplot(data = CPI_scores, aes(x = score_capabilities, y = GDPexp_capita, label = CPI_scores$country)) +
  crimson_theme() +
  geom_point(aes(),size=3, color="#A51C30") + geom_text_repel(aes(), hjust = -0.10, nudge_x = 0.05) +
  ggtitle("") +
  labs(x = "National Cyber Power Index (NCPI)" , y = "GDP per capita") 
                     
```



<!-- Note: spell check -->
<!-- Here are three ways to access spell checking in an rMarkdown document in rstudio: -->

<!-- A spell check button to the right of the save button (with "ABC" and a check mark). -->
<!-- Edit > Check Spelling... -->
<!-- The F7 key -->
<!-- A keyboard alternative to option 2 is alt + e + s. That is, while holding down the alt key, type e followed by s. -->







